Draft Visualizationa for Semester Project

### 2018-11-25 Visualizations/Draft Visualizations Template.Rmd

---
title: "Draft Visualizationa for Semester Project"
output: html_document
---
#Loading the Data and Necessary Packages
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
health <- read.csv("mentalsurvey_clean.csv")
```

@@

@@

@@

```{r}
#Put company size in order
ENumOrder  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
```

>>>>

---
title: "Draft Visualizationa for Semester Project"
output: html_document
---
#Loading the Data and Necessary Packages
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
#Insert the location of your data here, for example
health <- read.csv("mentalsurvey_clean.csv")
```

@@

####Crosstab Table

```{r}
#Put company size in order
CompanySize  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
#Create Cross-tab Table
APbCS <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., CompanySize)
head(APbCS)
```

####Proportions table

```{r}
#Create a proportions table by Row
prop.table(APbCS, 2)
```

####Chi-Squared Test

```{r}
#Do a chi-squared test
chisq.test(APbCS)
```

####Visualization of Data

```{r}
ggplot(health, aes(CompanySize, health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)) + geom_jitter(height = .3, width = .3) + ggtitle("Anonymity Protections For Mental Health Services") + xlab("Company Size") + ylab("Is Anonymity Protected?") 
```

####Interpretation of Results

The table and chart above show that across all company sizes, most respondents indicate that they do not know what their current company's anonymity policy is towards those using mental health services.  For companies of 1-5 employees, the next most common answer is "No" (anonymity is not protected). However, for companies larger than 5 employees, the results appear fairly consistent, with the majority of respondents (60-70 percent) indicating that they do not know anonymity policies, a sizable minority of respondents saying that anonymity is protected (25-32 percent), and less than 10 percent of respondents in each group saying anonymity is not protected. Based off of the chi-squared test, it is not clear if there is a statistically significant difference in anonymity policies of companies of different sizes.

@@

####Cross-tab Table

```{r}
#Add labels to tech company org
TLabel <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
levels = c(0, 1),
labels = c("No", "Yes"))
#Create a crosstab table
APbT2 <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., TLabel)
head(APbT2)
```

####Proportions table

```{r}
#Create a proportions table by Row
prop.table(APbT2, 2)
```

####Chi-Squared Test

```{r}
#Do a chi-squared test
chisq.test(APbT2)
```

####Visualization of Data

OPTION 1

```{r}
ggplot(health, aes(TLabel, health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)) + geom_jitter(height = .3, width = .3) + ggtitle("Anonymity Protections For Tech vs. Non-Tech Companies") + xlab("Is Employer Primarily Tech?") + ylab("Is Anonymity Protected?") 
```

OPTION 2

```{r}
#Run Counts
summary(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)
#Modify Labels
levels(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.) <- c("Don't Know Anonymity Policy", "Anonymity Not Protected", "Anonymity Protected")
#Check to make sure
summary(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)
```

```{r}
#Create Visualization
p3 <- ggplot(health, aes(x = TLabel))+geom_bar()+facet_wrap(~ health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)+ ggtitle("Anonymity Protections For Tech vs. Non-Tech Companies") + xlab("Is Employer Primarily Tech?") + ylab("Count") 
p3
```

####Interpretation of Results

The difference between primarily tech and non-primarily tech companies is not statistically significant in regards to anonymity policies for those seeking mental health services.  In both cases, the clear majority of those surveyed indicated that they do not know  their current company's anonymity policy is towards those using mental health services.  In both cases, the next most common response to the question is that anonymity is protected for those using mental health services.

@@
